
Code associated with an experiment concerned with examining the effects of storage method on fructose concentration

```{r}
library(ggplot2)
library(emmeans)
library(lme4)
library(tidyverse)
library(psych) 
library(stats) 
library(MASS)
library(car)
library(cowplot)
library(sjPlot)
library(ggpubr)
library(jtools)
library(plotly)

```

Including the KOD data

Importing the new data (with KOD)

```{r}
PRES_data_KOD <- read.csv(file = "PRES_01_R_KOD_June_2021.csv")
PRES_data_KOD$day <- as.factor(PRES_data_KOD$day)
str(PRES_data_KOD)


#low to high
PRES_data_KOD$treatment2 <- factor(PRES_data_KOD$treatment, levels = c("Crushed EtOH", "Whole EtOH", "Heat fixed", "Frozen", "KOD"))

str(PRES_data_KOD)

#change the order from High - Low
PRES_data_KOD$treatment3 <- factor(PRES_data_KOD$treatment, levels = c("KOD","Frozen","Heat fixed","Whole EtOH", "Crushed EtOH"))


```

Visualise the data
```{r}

ggplot(PRES_data_KOD, aes(x=treatment2, y= fructose_concentration))+ geom_boxplot() + facet_wrap(~day) + labs(x="", y=expression("Fructose concentration ("~mu*"g /"~mu*"L)")) + theme(axis.text.x = element_text(angle=45, hjust = 1)) 
#order that I would like is W_ETOH, C_ETOH, Frozen, HF


#have a graph where day is concatenated over one another (fill = day)

ggplot(PRES_data_KOD, aes(x=treatment3, y= fructose_concentration))+ geom_boxplot() + labs(x="Treatment", y=expression("Fructose concentration ("~mu*"g /"~mu*"L)"), fill = "Day") + theme_cowplot()

#theme(axis.text.x = element_text(angle=45, hjust = 1))+ geom_point(position = "jitter")
```

Plot fructose content
```{r}

fructose_content_pub <- ggplot(PRES_data_KOD, aes(x=treatment3, y= fructose_content))+ geom_boxplot() + labs(x="Treatment", y=expression("Fructose content ("*mu*"g)"), fill = "Day") + scale_y_continuous(limits = c(0,1000)) + theme(axis.title.x = element_text(vjust=-1.5)) 

#+ ylim(0,920)
#to save the plot as a ".svg" to add the statistical significance letters.

#save_plot("fructose_content_pub_cowplot.svg")
```

Run a GLM on the data
```{r}
PRES_KOD_glm <- glm(fructose_concentration ~ day+treatment, data = PRES_data_KOD)
Anova(PRES_KOD_glm)
#no significant effect with the interaction. 

#test to see if assumptions are okay

#Shapiro-Wilk normality test
shapiro.test(residuals(PRES_KOD_glm))

#violates normality

#Levene Test

leveneTest(residuals(PRES_KOD_glm), PRES_data_KOD$treatment) 
#Levene's test is > 0.05 - no detection of unequal variance. 

#trying to log the response variable fructose concentration (for normality)

PRES_KOD_log_glm <- glm(log(fructose_concentration) ~ day+treatment, data = PRES_data_KOD)
Anova(PRES_KOD_log_glm)
#no significant effect with the interaction. 

#test to see if assumptions are okay

#Shapiro-Wilk normality test
shapiro.test(residuals(PRES_KOD_log_glm))
#does not violate normality

#Levene Test

leveneTest(residuals(PRES_KOD_log_glm), PRES_data_KOD$treatment) 
#Levene's test is < 0.05 - not equal variance. However, it is not hugely below 0.05 and could be argued that the assumption of equal variance for the dependent variable for all groups 'could' be disregarded if you have equal sample sizes for each group. 

#examine post-hoc differences
comparisons_PRES_KOD <- emmeans(PRES_KOD_log_glm, pairwise ~ treatment)
comparisons_PRES_KOD

#no change in results from previously reported (without KOD)

```

There was a significant difference in fructose content of Ae. aegypti by storage method (χ2 = 59.1, df = 4, P < 0.001, Fig 3). Fructose content of Ae. aegypti, killed on the day of collection did not differ between frozen (P = 0.45) or heat-fixed (P = 0.33) treatments but was significantly higher compared to the fructose content in Ae. aegypti stored crushed (P < 0.0001) or whole in 80% ethanol (P < 0.0001). There was no significant difference in fructose content between Ae. aegypti stored crushed or whole in 80% ethanol (P = 0.24). For each storage method, there was no significant difference in fructose content of Ae. aegypti, after 7, 14 and 21 days in storage (χ2 = 0.37, df = 2, P = 0.83).  

```{r}
sessionInfo()
```

